Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-05-14 paper/paper.tex
NC of Bellman equation

\begin{mdframed}
  \textbf{ Neural correlates of the Bellman equation in the DMN:}
  ...
  \textbf{XXX Guillaume: I agree that this would be BIG!}
\end{mdframed}

>>>>

% neuroscience of Bellman equation
%\textbf{Neural correlates of the Bellman equation in the DMN:}
In neuroscience,
processing of ``goal-tree sequences''
has been linked to specific neural activity in the
dorsal prefrontal cortex (BA9) based on human brain-imaging experiments
\citep{koechlin1999role, koechlin2000dissociating}.
Sub-goal exploration may require multi-task switching between cognitive processes
as later parts of a solution
frequently depend on respective earlier steps of a given solution path, which
probably necessitates storage of expected intermediate outcomes.
``Cognitive branching'' operations for nested solution processing
are thus likely to
entail secondary reallocation of attention and working-memory resources.
The various advanced human mental abilities subserved by the DMN, such as
planning and abstract reasoning, can be viewed to involve some form of branching
to enable higher-order executive control.
Further neuroimaging experiments \citep{braver2002role} corroborated
the prefrontal DMN to subserve
``processes related to the management and monitoring of sub-goals while maintaining information in working memory''.
%
Moreover,
neurological patients with lesions in this DMN node were reported
to be impaired in aspects of realizing ``multiple sub-goal scheduling''
\citep{burgess2000cognitive}.
